\documentclass[10pt]{letter}
\usepackage[a4paper,margin=0.75in,footskip=0.25in]{geometry}
\usepackage{color}
\usepackage{multirow}
\pagenumbering{gobble}
\setlength\parindent{0pt}
\begin{document}
\textbf{Evin Sellin}
\hfill
evin.dev $\cdot$ (323) 327-7888 $\cdot$ evinism@gmail.com
\vspace{4px}
\hrule
\textbf{Work Experience}

\hspace*{2px}
\textbf{Senior Software Engineer}
\textit{Discord Inc, ML Platform}
\hfill 
\textbf{Jul 2022 - Jan 2024}
\begin{itemize}
  \item Proposed, designed, managed development of, and directly implemented the majority of Discord's LLM abstraction layer, enabling traceability, observability, and vendor agnosticism to all LLM usage.
  \item Deployed, scaled, and cut cost of serving of generative LLM features to full production traffic.
  \item Built a large variety of MLOps and infrastructural primitives, supporting a wide gamut of Discord's ML org goals. Partnered directly with client teams to solve business-critical cross-disciplinary problems in ML.
  % \item Enabled smooth pathways to transitioning from external OpenAI models to self-hosted models.
  %\item Enabled sub-hourly batch jobs to bridge the gap between realtime and batch.
  %\item Supported ML Engineer across several orgs, enabling them to do the best work they can.
\end{itemize}

\hspace*{2px}
\textbf{Senior Software Engineer} 
\textit{Vidora Inc.}
\hfill 
\textbf{Oct 2020 - May 2022}
\begin{itemize}
  \item Advocated for, designed, and implemented a real-time multi-armed bandit optimization system, nearly doubling top-of-funnel sales pipeline. System operating in production at 100qps at peak.
  \item Architected a global ML serving engine with real-time predictions served under 100ms.
  \item Authored and productionized MistQL, a language purpose-built for Vidora's client-side feature extraction.
  \item Shipped uplift modeling to Vidora's modeling platform. Completed a month under estimate.
  \item Built a CI/CD pipeline from the ground up, unearthing dozens of critical bugs.
\end{itemize}

\hspace*{2px}
\textbf{Software Engineer}
\textit{Google, YouTube Mobile Web Core}
\hfill 
\textbf{Dec 2018 - Jul 2020}
\begin{itemize}
  \item Bootstrapped process for safe conversion of 40k LOC JS codebase to TypeScript, using custom tooling I authored. System in use for over a year with contributions from nearly a dozen developers across multiple teams. Enabled conversion with zero production issues.
  \item Planned and executed the cleanup and removal of ~100k LOC codebase of highly volatile, business-critical server side Python with minimal production issues.
  \item Rebuilt YouTube mWeb's settings page from the ground up.
\end{itemize}

\hspace*{2px}
\textbf{Machine Learning Engineer}
\textit{Procore Technologies}
\hfill
\textbf{Jun 2018 - Dec 2018}
\begin{itemize}
  \item Researched, implemented, and integrated experimental machine learning models for Procore’s first customer-facing ML features, including content-aware image search for the construction domain.
\end{itemize}

\hspace*{2px}
\textbf{Software Engineer, Frontend}
\textit{Procore Technologies}
\hfill 
\textbf{Mar 2016 - Jun 2018}
\begin{itemize}
  \item Acted as primary maintainer and SME for most of Procore's web-based document viewers.
  \item Led technical direction through major performance and UX overhauls of some of Procore’s most used pages and features, saving at least \$250000 in churning contracts.
  \item Mentored peers across multiple product domains on practical web performance techniques.
\end{itemize}

\vspace{4px}
\hrule
\textbf{Open Source}

\begin{tabular*}{\linewidth}{ll@{\extracolsep{\fill}}r}
\textbf{MistQL} & \textit{www.mistql.com} & \textbf{Oct 2021} \\
\multicolumn{3}{l}{\hspace*{2px}Query language for JSON-like structures. Featured in Thoughtworks’ Tech Radar Vol 26} \\
\textbf{Lambda Explorer} & \textit{lambdaexplorer.com} & \textbf{Jun 2017} \\
\multicolumn{3}{l}{\hspace*{2px}Tutorial / REPL for the Lambda Calculus. Focus on contextual pedagogy. React + Typescript } \\
\end{tabular*}

\vspace{4px}
\hrule
\textbf{Publications}

\begin{tabular*}{\linewidth}{ll@{\extracolsep{\fill}}r}
\textit{Patent} & Computer System and Method for Predicting Risk Level of Punch Items & \textbf{Mar 2020} \\
% \textit{Blog} & \multicolumn{2}{l}{evinsellin.medium.com Articles primarily focusing on technical topics and satire.}
\end{tabular*}

\vspace{4px}
\hrule
\textbf{Technical Proficiencies}

\begin{tabular*}{\linewidth}{ll@{\extracolsep{\fill}}l}
  \textit{Languages} & Python, Typescript, JS, Rust, Terraform, Ruby, HTML/CSS, and others \\
  \textit{ML} & Pytorch, Tensorflow, sklearn, various serving frameworks, OpenAI, and others \\
  \textit{Tooling} &  Kubernetes, GCP, AWS, React, Rails, Django, Postgres, various NoSQLs, and others \\
\end{tabular*}

\vspace{4px}
\hrule
\textbf{Education}

\hspace*{2px}
\textbf{B.S. Computer Engineering}
\textit{University of California, Santa Barbara}
\hfill
\textbf{2011 - 2015, Completed 2018}

\end{document}
